Co-moving stars in \textsl{Gaia DR1}: a catalog of genuine co-moving star pairs from low-resolution spectroscopic follow-up

### 2017-05-17 paper/comoving-followup.tex
brainstorming intro and structure

\section{Observations and Data reduction}\label{sec:reduction}

@@

>>>>

Outline:
- Stars form in clusters, chemically homogeneous at some level
- Clusters generally disrupt slowly through a process that preserves initial
  clustering in conserved quantities but destroys phase coherence
- Most significant process is probably tidal heating
- Dissolved clusters are therefore useful dynamical tracers of mass distribution
- In Galactic halo, globular clusters
- In disk, hope is to use chemical signatures to connect stars, then can use
  dynamics to reconstruct birth clusters, infer mass distribution / evolution
- Clusters have advantage of many stars per cluster, but fewer clusters
- Wide binary stars are little potentiometers themselves - only N=2, but are far
  more numerous as a population
- Long-term goal is to study the separation distribution of wide-binaries as a
  function of age and Galactic orbit distribution (disk vs. halo)
    - Is there a separation truncation?
    - Can that be described just from Galactic tides, or need perturbers?
- Also useful for stellar models: should have same age, chemistry, but need to
  test this
    - Chemical homogeneity tested with few open clusters - wide binaries another
      test
    - Need sample of confirmed widely-separated binaries, follow-up to get
      detailed abundances
    - Need way to verify that widely separated stars are physically associated,
      via kinematics

Most stars form in clusters with small dispersions in position, velocity, and
(likely) small initial spreads in chemical abundances.
Once a given cluster is visibly dispersing or fully dispersed, the former member
stars retain chemical and kinematic signatures of their birth cluster

, though
the kinematic mapping is non-trivial because of phase-mixing.

become
useful

Widely-separated co-moving stars are expected to form from the dissolution of
birth star clusters

\section{Data}\label{sec:data}

\subsection{Sample selection}\label{sec:sample}

Target sample taken from ... Oh et al.

Briefly, ...

TGAS roughly XX\% complete to 200 pc with parallax SNR cut.

Oh catalog have a high likelihood-ratio cut, but that should be unbiased (right?)

Randomly sample from that, subject to observational constraints.

\subsection{Observations and Data reduction}\label{sec:reduction}

@@

- Comparing repeat visits on subsequent nights, systematic ~20 km/s
    - see notebook "Compare RVs with previous measurements"
